A generalized definition of multidimensional item response theory parameters

### 2022-11-21 output/paper_draft/paper_M2PLM_parameters.Rmd
Adds change of basis matrix in test space (keeping norm invariant)

The basis $`r ITEM_SPACE_BASIS_EQ`$ of $`r TEST_SPACE`$ is such that
$`r ITEM_TRANSF_MATRIX_EQ`$ (see Equation \@ref(eq:discr-vector-std)).
Thus, similarly to equation \@ref(eq:dir-cos-vec),
the vector of direction cosines of a vector in $`r TEST_SPACE`$
can be defined as

>>>>

Let $`r LS_STD_BASIS`$ be the standard basis of $`r TEST_SPACE`$.
<!-- # TODO: Can the standard basis of \Alpha be also \mathcal{E}? Otherwise, may I use \mathcal{E} instead? -->
Then, $`r BASIS_CHANGE_TS_EQ`$ is the change of basis matrix and
<!-- # TODO: Result pending of demonstration? -->
$`r DISCR_VECTOR_STD_MOD_EQ`$.

Applying propositon 1,
